---
title: "Seattle Reign FC Marketing Strategies Consulting"
author: "Wei Li"
date: "March, 21st, 2019"
output: slidy_presentation
---

```{r, message = FALSE, echo = FALSE, error = FALSE, warning = FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 

# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)

```

```{r echo=FALSE, include=FALSE}
library(tidyverse)
load("workspace.RData")
```

About this research
=========================================

+ Focus: Impact of the present marketing strategies

+ Purpose: Provide suggestions for Seattle Reign marketing department

+ Data is from survey

+ Consisting of four sections about past attendance behaviors, behavior intentions, psychographics, and demographics

+ 684 useable survey responses obtained

+ Findings and suggestions following are all from this data set


Effectiveness of All present Marketing Strategies
=========================================
```{r echo=FALSE}
G1
```

Season Tickets Selling
=========================================
```{r echo=FALSE}
G2
```

Best Game Time for Audiences
=========================================
```{r echo=FALSE}
G3
```

Conclusion and Suggestions Based on Previous Analysis
=========================================

* Invest more efforts and money in the promoting activities: 
    + Emails and Internet ads
    + Providing discounts, especially post-matches discount
    + Encourage audience to come together with companions
    + Media publicity about team matches, especially Facebook posts
* Promote season tickets sold in these 4 groups:
    + Household income ranging from $200,000 to $299,999
    + Household income ranging from $100,000 to $149,999
    + Household income ranging from $60,000 to $79,999
    + Household income ranging and from $20,000 to $39,999
* Game time:
    + Arrange more events on Saturday 4 pm, Saturday 1 pm and Sunday 4 pm
    + For events arranged on Wednesday evenings or Sunday evenings, provide discount

